\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-11-20 exps.tex
changin exp section

We have carried out a number of experiments on a set of applications
with real-time constraints. The benchmark set is shown in
Table~\ref{fig:comparison}. HRCTS is the human response system described
in Figure~\ref{fig:1}. AECS (Access and Environmental Control System) is
an application that controls an intelligent room environment described
in~\cite{aecs_ispa}. Motor is a stepper motor controller
from~\cite{Bourke2009a}. Robot is an industrial automation application
that consists of two manufacturing belts and a robotic arm that splits
goods according to their volumes. HRCTS consists of 2 CDs, but only one
with real-time delays. AECS also has 2 CDs; CD1 consist of a single
delay statement, while CD2 has 2 delay statements. Robot and Motor both
are synchronous programs with 1 and 5 delay statements,
respectively. All these examples are written in the SystemJ
language. The requirement to have deterministic or non-deterministic
delays varies between each benchmark. These delay requirements are shown
in Table~\ref{fig:comparison} (\texttt{M..N}).

>>>>

We have carried out a number of experiments on a set of applications
with real-time constraints. The benchmark set is shown in
Table~\ref{fig:comparison}. HRCTS is the human response system described
in Figure~\ref{fig:1}. AECS (Access and Environmental Control System) is
an application that controls an intelligent room environment described
in~\cite{aecs_ispa}. The system interacts with two external timers
through input/output signals in order to measure how long the entrance
door to the room is being opened and time the illegal presence (e.g.
intruder) that is being detected. The program has been modified such
that the delay constructs are used instead of external timers as shown
in~\ref{delaycode}.

\begin{figure}[h!]
	\begin{SubFloat}{\label{delaycode:a}sss}
		\centering
		\begin{minipage}[b]{0.3\linewidth}
			\footnotesize
\begin{verbatim}
emit TimerTriggered;
trap(T){
  abort(DoorOpened){
    await(TimeOut);
    exit(T); 
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\hspace{1cm}%
	\begin{SubFloat}{\label{delaycode:b}sss}
		\centering
		\begin{minipage}[b]{0.3\linewidth}
			\footnotesize
\begin{verbatim}
// No emit statement
trap(T){
  abort(DoorOpened){
    delay(2.4 .. 7.4772 ms);
    exit(T);  
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\caption{www}
\label{delaycode}
\end{figure}

Motor is a stepper motor controller from~\cite{Bourke2009a}. Robot is an
industrial automation application that consists of two manufacturing
belts and a robotic arm that splits goods according to their volumes.
HRCTS consists of 2 CDs, but only one with real-time delays. AECS also
has 2 CDs; CD1 consist of a single delay statement, while CD2 has 2
delay statements. Robot and Motor both are synchronous programs with 1
and 5 delay statements, respectively. All these examples are written in
the SystemJ language. The requirement to have deterministic or
non-deterministic delays varies between each benchmark. These delay
requirements are shown in Table~\ref{fig:comparison} (\texttt{M..N}).
